Implications of afforestation policies for global markets

### 2023-06-01 paper.Rmd
Update paper.Rmd

Scenarios
1) Full attainment of AFR100 pledges as part of Bonn Challenge:  This says that there will be a 127.81 million hectare increase in forest area just in Sub-Saharan Africa by 2030 [@bonn2023]. To see the list of countries and the hectares pledged, please view Scenario 1 of the Excel document "Bonn Challenge-Africa".
2) Partial attainment of AFR100 pledges as part of Bonn Challenge:  This scenario analyzes full attainment for nations with conflict severity level less than or equal to limited and 0% attainment for regions with a higher conflict severity rating. Using this measure, there would only be a 54.95 million hectare increase in forest area by 2030 [@bonn2023]  [@acled2023]. To see the list of countries and the hectares pledged, please view Scenario 2 of the Excel document "Bonn Challenge-Africa".
3) Full attainment of UN strategic plan for forests 2030 (UNFF):  This says that all deforestation will halt and there will be a 3% (120 million hectare) increase in forest area worldwide by 2030 [@sewell2020].
4) 
5) Full attainment of goals of Bonn Challenge and New York Declaration on Forests:  This says that all deforestation will halt and there will be a 350 million hectare increase in forest area worldwide by 2030 [@sewell2020].

>>>>

Scenarios
1) Full attainment of AFR100 pledges as part of Bonn Challenge: This says that there will be a 127.81 million hectare increase in forest area just in Sub-Saharan Africa by 2030 [@bonn2023]. To see the list of countries and the hectares pledged, please view Scenario 1 of the Excel document "Bonn Challenge-Africa".
2) Partial attainment of AFR100 pledges as part of Bonn Challenge: This scenario analyzes full attainment for nations with conflict severity level less than or equal to limited and 0% attainment for regions with a higher conflict severity rating. Using this measure, there would only be a 54.95 million hectare increase in forest area by 2030 [@bonn2023]  [@acled2023]. To see the list of countries and the hectares pledged, please view Scenario 2 of the Excel document "Bonn Challenge-Africa".
3) Full attainment of Latin America pledges as part of Bonn Challenge: This says that there will be a 33.64 million hectare increase in forest area by 2030 [@bonn2023]. To see the list of countries and the hectares pledged, please view the Latin America tab of the Excel document "Bonn Challenge-Other Regions".
4) Full attainment of tropical nations' pledges as part of Bonn Challenge: This says that there will be a 182.30 million hectare increase in forest area by 2030 [@bonn2023]. To see the list of countries and the hectares pledged, please view the Tropical Forest tab of the Excel document "Bonn Challenge-Other Regions". Nations that lie in both tropical and sub-tropical zones and taken to be tropical.
5) Full attainment of UN strategic plan for forests 2030 (UNFF): This says that all deforestation will halt and there will be a 3% (~120 million hectare) increase in forest area worldwide by 2030 [@sewell2020]. This will be modeled as a uniform 3% increase in forested area across all nations.
6) Expansion of UN strategic plan for forests: This says that all deforestation will halt and there will be a 15% (~600 million hectare) increase in forest area worldwide by 2030 [@sewell2020]. This will be modeled as a uniform 15% increase in forested area across all nations.
